### 2023-04-12 definitions.tex
up

\begin{definition}
A {\em reset VASS} in dimension $d$ ($d$-dim Reset VASS for short) is a finite 
% $\mathds{Z}^d$
labeled directed graph $V = (Q,T)$, where $Q$ will be referred to as the {\em control states} of $V$, and where 
%$T \subseteq Q \times \mathds{Z}^d \times Q$
$T \subseteq Q \times Op \times Q$
 will be referred to as {\em control transitions} of $V$. 
where $Op = \{ add(\textbf{z}) | \textbf{z} \in \mathds{Z}^d\} \cup 
		\{ reset(i) | i \in \{1,\ldots,d\} \}$.
\end{definition}

@@

\begin{samepage}
\problemx{Reset $d$-VASS zero reachability}
{A reset $d$-VASS $V=(Q,T)$, $q(\textbf{u}) \in Q \times \N^d$}
{$\exists p \in Q ~ q(\textbf{u}) \to^* p(\textbf{0})$? \\}
\end{samepage}

>>>>

\begin{definition}
A {\em Reset VASS} in dimension $d$ ($d$-dim Reset VASS for short) is a finite 
% $\mathds{Z}^d$
labeled directed graph $V = (Q,T)$, where $Q$ will be referred to as the {\em control states} of $V$, and where 
%$T \subseteq Q \times \mathds{Z}^d \times Q$
$T \subseteq Q \times Op \times Q$
 will be referred to as {\em control transitions} of $V$. 
where $Op = \{ add(\textbf{z}) | \textbf{z} \in \mathds{Z}^d\} \cup 
		\{ reset(i) | i \in \{1,\ldots,d\} \}$.
\end{definition}

@@

\begin{samepage}
\problemx{$d$-dim Reset VASS zero reachability}
{A $d$-dim Reset VASS $V=(Q,T)$, $q(\textbf{u}) \in Q \times \N^d$}
{$\exists p \in Q ~ q(\textbf{u}) \to^* p(\textbf{0})$? \\}
\end{samepage}
